\pagestyle{plain}
\thispagestyle{empty} %no header 
% The title of my cv
\begin{center}
	\Large{\textsc{Ruihao Bi}} \\
	\normalsize {School of Science, Westlake University, Zhejiang, P.R.China, 310024} \\
	Telephone: {+86 18605025530} $|$
	Email: {\href{mailto:biruihao@westlake.edu.cn}{biruihao@westlake.edu.cn}} $|$
	\href{https://github.com/ruihao69}{Github} $|$ \href{https://github.com/ruihao69/brh-cv}{Detailed CV}  \\
\end{center}

%%%
\sectionheading{Education}
\sectionrule
\subsectionheading{School of Science, Westlake University (WLU)}{Hangzhou, China}

\noindent Graduate student (Wenjie, Dou Group) \hfill {Sept. 2022 -- now}
\begin{itemize}
	\item Selected Coursework:\\
	      Quantum Chemistry (A), Chemical Kinetics \& Reaction Dynamics (A), Spectroscopy and Group Theory (A), Quantum Mechanics of Open Systems (A)
\end{itemize}

\subsectionheading{College of Chemistry, Xiamen University (XMU)}{Xiamen, China}

\noindent Research Assistant (Jun, Cheng Group) \hfill {Jul. 2021 -- Jun. 2022}

\noindent Bachelor of Chemistry \hfill {Sept. 2017 -- Jun. 2021}

\begin{itemize}
	\item $\mathrm{1^{st}}$ Year: College of Materials, $\mathrm{2^{nd}}$--$\mathrm{4^{th}}$ Year: College of Chemistry.
	\item Overall GPA: 3.79/4.00, Major GPA: 3.85/4.00, Rank: 3/96.
	\item English skill: TOEFL iBT: 103 (R30, L29, S21, W23), tested in Nov. 2021.
	\item Selected Coursework:\\
	      Calculus I (100/100, top 1\%), Calculus II (95/100, top 2\%), Physics I (93/100, top 1\%), Physical Chemistry II (95/100, top 3\%), Chemical Kinetics \& Reaction Dynamics (95/100, top 1\%)
\end{itemize}

\vspace{5mm}
%%%
\sectionheading{Academic Experience}
\sectionrule

\subsectionheading{Nuclear Quantum Effects in the Dynamics of Electron Transfer near Metal Surfaces}{Sept. 2022 -- now}

{\noindent Advisor: Prof. Wenjie, Dou  \hfill \href{https://dougroup.westlake.edu.cn/index.html}{Dou Group Website}}

\begin{itemize}
	\item Developing electronic friction based methods for real time dynamics of electron transfers near meal surface, with special foucuses on nuclear quantum effects, i.e., ZPE and tunneling.
	\item Prediction of tunneling rates for electron transfer near metal surfaces.
\end{itemize}
\vspace{5mm}

\subsectionheading{Study of stability of different surface hydroxyl terminations for \ce{SrFeO_{3-\delta}}}{Feb. 2022 -- May. 2022}

{\noindent Advisor: Prof. Jun, Cheng  \hfill \href{https://cheng-group.net}{Cheng Group Website}}

\begin{itemize}
	\item Ab inito. electronic structure calculations (DFT) of bulk and surfaces SrFeO3-x. Study the formation energy of various defects.
\end{itemize}
\vspace{5mm}

\subsectionheading{MLP of \ce{TiO2} Water Interface Model and its Application }{Jul. 2021 -- now}


{\noindent Advisor: Prof. Jun, Cheng  \hfill \href{https://cheng-group.net}{Cheng Group Website}}


\begin{itemize}
	\item Trained DeePMD mechine learning force field for TiO2-water interface geometries, with witch we studied:
	\item \hkl[1-11] step-edge induced water molecule dissociations and double-row pattern;
	\item Adsorption water dissociation predicted by MD depends on the slab size, precisely, \# of TiO2 tri-layers.
\end{itemize}
\vspace{5mm}


\subsectionheading{Study Towards the Synthesis of Clionastatin B}{Jun. 2019 -- May 2021}

{\noindent Advisor: Prof. Yandong, Zhang  \hfill \href{https://zhanglab.xmu.edu.cn/}{Zhang Group Website}}

\begin{itemize}
	\item Trained organic lab skills for natural product synthesis.
	\item Study of a conformation driven facial-selective epoxydation reaction and a tertiary alcohol dehydration.
\end{itemize}


\vspace{5mm}

\sectionheading{Professional Skills}
\sectionrule
{\noindent \textbf{Programming skills:} }{shell, Python, C++, Cython}

{\noindent \textbf{Professional Softwares: }{DeePMD-kit, DPGEN, CP2K, VASP, LAMMPS, VMD, MDAnalysis}}

%%%
\clearpage
\sectionheading{Selected Awards}
\sectionrule

\begin{itemize}
	\item Wang Laoji Scholarship, XMU (2/96) \hfill Apr. 2021.
	\item Successful Participant of Mathematical Contest in Modelling \hfill May 2020.
	\item Elite Undergraduate Program of Chemistry Scholarship, XMU (15/168).

	      \hspace*{\fill}2018--2021, 4 times
	\item Scholarship of Academic Excellence, XMU. (10/168) \hfill Mar. 2018.
\end{itemize}

\vspace{5mm}

\sectionheading{List of publications}
\sectionrule
\nocite{*} % Include all items from the .bib file
\printbibliography[heading=none] % Print the list of publications
