% !TEX program = xelatex
% !TEX encoding = UTF-8 Unicode

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Medium Length Professional CV - RESUME main.tex
%
% Original header:
% Copyright (C) 2010 by Trey Hunner 
%
% Copying and distribution of this file, with or without 
% modification, are permitted in any medium without royalty 
% provided the copyright notice and this notice are 
% preserved. This file is offered as-is, without any warranty.
%
% Modified by Rui-Hao Bi (2024-07).
%
% Rui-Hao Bi acknowledges the awesome work of:
%
% - Trey Hunner and www.LaTeXTemplates.com
% - Hongtao Hao (https://github.com/hongtaoh)
% - N. Gibson (CIS Grad Template (Dev) on Overleaf)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{resume} 

\usepackage{enumitem}
\usepackage{etaremune}  % For reverse enumeration
\usepackage[version=4]{mhchem}

% for publication list, use chem-acs style  
\usepackage[
    backend=biber,%
    style=phys,%
    maxnames=99,%
]{biblatex}
\addbibresource{publications.bib}

\renewcommand*{\mkbibnamegiven}[1]{%
  \ifitemannotation{highlight}
    {\textbf{#1}}
    {#1}}

\renewcommand*{\mkbibnamefamily}[1]{%
  \ifitemannotation{highlight}
    {\textbf{#1}}
    {#1}}


%-----------------------------------------------------------
%   PERSONAL INFORMATION: name, phone, email, address
%-----------------------------------------------------------
\name{Rui-Hao Bi} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+(86) 18605025530 \\ Hangzhou, Zhejiang, China} % Your phone number and email
\address{\href{mailto:biruihao@westlake.edu.cn}{biruihao@westlake.edu.cn} \\ \href{https://github.com/ruihao99}{https://github.com/ruihao99}}  %

\begin{document}

%-----------------------------------------------------------
%   EDUCATION
%-----------------------------------------------------------
\begin{rSection}{Education}
    \lrone{Westlake University (WLU)}{Hangzhou, China} \\
    \lrtwo{Ph.D. Candidate in Chemistry}{Aug 2022 -- Jun 2027 (expected)}
    \begin{itemize}[noitemsep, nosep]
        \item Completed all required coursework and successfully passed defended thesis proposal (Dec. 2024).
    \end{itemize}

    \lrone{Xiamen University (XMU)}{Xiamen, China} \\
    \lrtwo{B.S. in Chemistry}{Sep 2017 -- Jun 2021}
    \begin{itemize}[noitemsep, nosep]
        \item GPA: 3.79/4.00 (Rank: 3/97); Elite Undergraduate Program (top 15\%).
    \end{itemize}
\end{rSection}

%-----------------------------------------------------------
%   RESEARCH EXPERIENCE
%-----------------------------------------------------------
\begin{rSection}{Research Experience}
    \lrone{Westlake University (WLU)}{Hangzhou, China} \\
    \lrtwo{Advisor: Prof. Wenjie Dou}{Aug 2022 -- Jun 2027 (expected)}
    \begin{itemize}[noitemsep, nosep]
        \item (Proposed) Thesis: The treatment of electronic-vibrational interactions: from methods to applications.
        \item (Ongoing) Spin-lattice relaxtion: strong coupling effect in realistic materials.
        \item \emph{Ab. initio.} Photophysics simulation with high-level coupled cluster quantum chemistry.
        \item The perturbative and numerically exact treatment of spin-lattice relaxtion.
        \item Nonadiabatic dynamics at metal interfaces: nuclear quantum effect and orbital surface hopping (model study).
    \end{itemize}

    \lrone{Xiamen University (XMU)}{Xiamen, China} \\
    \lrtwo{Advisor: Prof. Jun Cheng}{Jun 2021 -- Jun 2022}
    \begin{itemize}[noitemsep, nosep]
        \item \ce{TiO2} interface water dissociations and hydrogen bond structures accelerated by Machine Learning.
    \end{itemize}

    \lrone{Xiamen University (XMU)}{Xiamen, China} \\
    \lrtwo{Advisor: Prof. Yandong Zhang}{Jun 2019 -- May 2021}
    \begin{itemize}[noitemsep, nosep]
        \item Thesis: Studies on Several Reactions in the Synthesis of Marine Halogenated Natural Products Clionastatins
    \end{itemize}
\end{rSection}


%-----------------------------------------------------------
%   SELECTED PUBLICATIONS
%-----------------------------------------------------------
\begin{rSection}{Selected Publication List}
    \textbf{Nonadiabatic dynamics}
    \begin{enumerate}[series=myenum]
        \item \fullcite{bi2026accessing} \showpdf{https://arxiv.org/pdf/2604.05734} \showdataset{https://doi.org/10.6084/m9.figshare.31866094}
        \item \fullcite{bi2026generalized} \showpdf{https://arxiv.org/pdf/2603.01458}
        % \item \fullcite{liu2026projection} \showpdf{https://arxiv.org/pdf/2602.10629}
        % \item \fullcite{han2026two} \showpdf{https://arxiv.org/pdf/2601.03863}
        % \item \fullcite{liu2025absorption} \showpdf{https://arxiv.org/pdf/2506.07430}
        % \item \fullcite{wang2025mixed} \showpdf{https://arxiv.org/pdf/2509.14248}
        \item \fullcite{zhou2025tunable} \showpdf{https://arxiv.org/pdf/2506.04885} 
        \item \fullcite{bi2025universal} \showpdf{https://arxiv.org/pdf/2504.00649} \showcode{https://doi.org/10.5281/zenodo.15393237}
        \item \fullcite{Maosh2025} \showpdf{https://arxiv.org/pdf/2412.19097} (Contributed equally)
        \item \fullcite{Bispinlattice2024} \showpdf{https://arxiv.org/pdf/2404.04803}
        \item \fullcite{Birpmd2024} \showpdf{https://arxiv.org/pdf/2311.08779}
    \end{enumerate}

    \noindent\textbf{Machine Learning Accelerated Molecular Dynamics for Electrochemical Interfaces}
    \begin{enumerate}[resume*=myenum]
        \item \fullcite{Sun2024} \showcode{https://github.com/robinzyb/ECToolkits}
        \item \fullcite{Zhuang2022} \showcode{https://github.com/robinzyb/ECToolkits} (Contributed equally)
    \end{enumerate}
\end{rSection}

%-----------------------------------------------------------
%  Posters and talks
%-----------------------------------------------------------
\begin{rSection}{Posters \& Talks}
\begin{enumerate}
    \item \emph{The 35th Chinese Chemical Society (CCS) Congress}, ``Benchmarking RI-CC2 for Nonadiabatic Dynamics: The Ultrafast Internal Conversion in Pyrazine'', Chongqing, Apr. 2026, \textbf{poster} \showpdf{https://github.com/ruihao99/brh-cv/blob/master/posters_and_talk/CCS_35_talk_20260412.pdf}.
    \item \emph{The 14th Conference on Computational Statistical Mechanics of Complex Systems (CSMCS2025)}, ``Exact quantum dynamics of open systems from memory kernel coupling theory: computation of higher-order moments'', Shenzhen, Nov. 2025, \textbf{talk} \showpdf{https://github.com/ruihao99/brh-cv/blob/master/posters_and_talk/CSMCS2025_talk_20251107.pdf}.
    \item \emph{The 19th National Conference on Chemical Dynamics (NCCD19)}, ``Exact quantum dynamics of open systems from memory kernel coupling theory: computation of higher-order moments'', Chun'an, Oct. 2025, \textbf{poster} \showpdf{https://github.com/ruihao99/brh-cv/blob/master/posters_and_talk/NCCD_19_poster_20250919.pdf}.
    \item \emph{The 11th Triennial Congress of the International Society for Theoretical Chemical Physics (ISTCP)}, ``Describing Nuclear Quantum Effects in Coupled Nuclear-Electron Dynamics at Gas-Metal Surface'', Qingdao, Oct. 2024, \textbf{poster} \showpdf{https://github.com/ruihao99/brh-cv/blob/master/posters_and_talk/ISTCP_11_poster_20241015.pdf}.
\end{enumerate}
\end{rSection}




%-----------------------------------------------------------
%   AWARDS AND HONORS 
%-----------------------------------------------------------
\begin{rSection}{Selected Awards And Honors}
    \begin{itemize}[noitemsep, nosep]
        \item Best Poster Award, 11th Triennial Congress of the International Society for Theoretical Chemical Physics (ISTCP, 9 / \emph{ca.} 280), \hfill Oct. 2024.  
        \item National Scholarship, WLU (3 / School of Science), \hfill Oct. 2024. 
        \item Wang Laoji Scholarship, XMU (2/96) \hfill Apr. 2021.
        \item Successful Participant of Mathematical Contest in Modelling (MCM)$^\copyright$ \hfill May 2020.
        \item Elite Undergraduate Program of Chemistry Scholarship, XMU (15/168)
              \hspace*{\fill}2018--2021, 4 times.
        \item Scholarship of Academic Excellence, XMU (10/168) \hfill Mar. 2018.
    \end{itemize}
\end{rSection}


%-----------------------------------------------------------
%   TECHINICAL STRENGTHS	
%-----------------------------------------------------------
\begin{rSection}{Computer and Language Skills}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
    Programming \& Software: & Python (mainly), C/C++, Fortran, MPI, CP2K, Q-Chem (developer) \\
    Language: & Mandarin Chinese (native), English (proficient, TOEFL iBT: 103, dated Nov. 2021)
\end{tabular}
\end{rSection}



%-----------------------------------------------------------
%   Teaching and Internships	
%-----------------------------------------------------------
\begin{rSection}{Teaching and Internships}
    \lrone{Westlake University}{Hangzhou, China} \\
    \lrtwo{Teaching assistant}{Sep 2023 -- Jan 2024} 
    \begin{itemize}[noitemsep, nosep]
        \item Tutoring duty for the Undergraduate "Computer and Programming" course (instructor: Prof. Yue Zhang).
    \end{itemize}

\end{rSection}


\end{document}
